Visualising gene differences based on read alignments

### 2022-02-22 analysis/GeneLossComparisonReads.Rmd
add some more changes
Make order of plot nicer

  theme(legend.position = "None",
  axis.text.y = element_text(face = "italic")) +
  scale_color_brewer(palette='Dark2') +
  ylab('Gene size difference (%)') +
  xlab('Species') +
  coord_flip()
ndh_chl_p
```

@@

```{r fig.width=10}
patchwork <- (eth_p + stom_p) / (ndh_p + ndh_chl_p)
# patchwork[[2]] = patchwork[[2]] + theme(axis.text.y = element_blank(),
#                                         axis.ticks.y = element_blank(),
#                                         axis.title.y = element_blank() )
# patchwork[[1]] = patchwork[[1]] + theme(axis.text.y = element_blank(),
#                                         axis.ticks.y = element_blank(),
#                                         axis.title.y = element_blank() )
patchwork+ plot_annotation(tag_levels = "A")
```

>>>>

  theme(legend.position = "None",
  axis.text.y = element_text(face = "italic")) +
  scale_color_brewer(palette='Dark2') +
  ylab('Gene size similarity (%)') +
  xlab('Species') +
  coord_flip()
ndh_chl_p
```

@@

```{r fig.width=10}
patchwork <- (eth_p + stom_p) / ( ndh_chl_p + ndh_p )
# patchwork[[2]] = patchwork[[2]] + theme(axis.text.y = element_blank(),
#                                         axis.ticks.y = element_blank(),
#                                         axis.title.y = element_blank() )
# patchwork[[1]] = patchwork[[1]] + theme(axis.text.y = element_blank(),
#                                         axis.ticks.y = element_blank(),
#                                         axis.title.y = element_blank() )
patchwork+ plot_annotation(tag_levels = "A")
```
